\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-28 Supplement.tex
edits
edits
edits
table formatting

\flushleft{\large{Vann \emph{et al.}: Variation in teosinte at the \emph{tb1} locus}}

@@

@@

\begin{longtable}{@{\extracolsep{\fill}}llllllllll@{}}
  \hline\hline %inserts double horizontal lines

@@

 \textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule

@@

% Table S2. Mays sampling
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering

@@

    \begin{tabular}{ccc}
 %   \toprule
    Accession & Number of alleles sampled & \emph{Hopscotch} Frequency \\
 %   \midrule

@@

    \end{tabular}

@@

\end{table}

>>>>

@@

\clearpage

@@

%\setlength\LTleft{-30pt}            % default: \fill
%\setlength\LTright{-30pt}           % default: \fill
\begin{longtable}{llllll}

@@

& \textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule

@@

% Table S2. Mays sampling
\begin{longtable}{lcc}

@@

& \textbf{Accession} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} \\\toprule

@@

@@
